---
title: "Estuarine and Wetland: week one exercise"
output: webex::webex_default
author: "Nyamisi Peter"
date: "12/4/2020"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!requireNamespace("webex")) {
  stop("You must have the 'webex' package installed to knit HTML from this template.\n   devtools::install_github(\"psyteachr/webex\")")
} else {
  library("webex")
}
```

# Instructions
> Please note that the appearance of the `text box` and `pull-down` changes from red to blue colours when you enter the correct answer. 

# WEEK ONE

1. Explain what do you understand by the word *Estuarine* `r fitb("Estuarine is.... ")`

Create fill-in-the-blank questions using `fitb()`, providing the answer as the first argument.

- 2 + 2 is `r fitb("4")`

You can also create these questions dynamically, using variables from your R session.

```{r echo = FALSE}
x <- sample(2:8, 1)
```

- The square root of `r x^2` is: `r fitb(x)`

- the sum of `r c(2,5,8,3)` is `r fitb(sum(c(2,5,8,3)))`

- What is the word for an area where freshwater meet salt water? `r fitb("Estuarine", ignore_case = TRUE)`


- What is the largest estuarine system along the coastal water of Tanzania? `r mcq(c("Ruvuma", "Ruvu", answer = "Rufiji"))`

- Of `r mcq(c("Coral", "Seagrass", answer = "Mangrove"))` is the habitat found only in the estuarine?

- Can estuarine have salinity above 34 psu? `r torf(FALSE)`

